### 2018-11-07 inst/table_tennis_serve.Rmd
slight rewording for clarity

The difference in support, ```delta_support```, is about 2.62 which
exceeds Edwards's two-units-of-support criterion.  The likelihood
ratio LR is about 13.8, and Wilks's theorem gives us that
$\Lambda=2\log(LR)$ is distributed as chi-squared with one degree of
freedom; the tail area, pval, is about 0.022 which gives us a
significant result.

Further, note that our estimated strengths as obtained by MLE allow us
to assess what might happen when A plays C (which was not observed).
If A serves, we would have $A+S:C\simeq 0.24+0.45:0.16\equiv 69:16$,
or A wins with probability of about $0.81$.  If C serves we have
$A:C+S\simeq 0.24:0.16+0.45\equiv 24:61$, so A wins with a probability
of about $0.28$.

>>>>

The difference in support, ```delta_support```, is about 2.62 which
exceeds Edwards's two-units-of-support criterion.  The likelihood
ratio LR is about 13.7, and Wilks's theorem gives us that
$\Lambda=2\log(LR)$ is distributed as chi-squared with one degree of
freedom; the tail area, pval, is about 0.022 which gives us a
significant result.

Further, note that our maximum likelihood estimate for strengths
allows us to assess what might happen when A plays C (which was not
observed).  For convenience, here is the evaluate:

```{r}
maxp(H)
```

If A serves, we would have $A+S:C\simeq 0.24+0.45:0.16\equiv 69:16$,
or A wins with probability of about $0.81$.  If C serves we have
$A:C+S\simeq 0.24:0.16+0.45\equiv 24:61$, so A wins with a probability
of about $0.28$.
